\chapter{Project management}

\section{Project name}
Project name is important project identificator. It should summarize main project goal or functionality. In real project, is often a trademark, or reflects the name of the company.

In this section, we will describe the process of choosing a name for the project. First of all, we made a list of words, that we can use in the project name. These words describe project funcionality or goal.

Words that can be used in project name: master, console, web, text, keyboard

We used the list of words and brainstorming session on a meeting for compiling a list of project name candidates:

Candidate project names: console 2.0, wonsole, wensole, websole, werminal, interCLI

After discussion we chose the name \emph{Wonsole}. Project name can be sometimes little confusing, so we added the subtitle: \emph{The new web console for power users.}

\section{Team roles}
\begin{tabularx}{\textwidth}{ | l | X | l | }
  \hline
  \textbf{Role} & \textbf{Description} & \textbf{Assignee} \\ 
  \hline
  Team leader & Is responsible for administrative tasks and makes the final decisions. & Ivo \\ 
  \hline
  Scrum Master & Shields the development team from external distractions and enforces the Scrum scheme.  & Ivo \\ 
  \hline
  Customer Contact & Handles communication with the customer. The customer should contact this person regarding general requests, questions and reminders. & Ivo (backup Martin) \\ 
  \hline
  Advisor Contact & Handles communication with the advisor. The advisor should contact this person regarding general requests, questions and reminders.  & Ivo (backup Martin) \\ 
  \hline
  System Architect & Is responsible for the system architecture including distinctions and relations between subsystems and general code design choices. & Martin \\ 
  \hline
  Code Master & Overall responsible for code management and structure. Managing branches in Git repository. & Oddvar  \\ 
  \hline
  GUI Designer & Is responsible for the layout and design of graphical user interfaces. & Oddvar \\ 
  \hline
  Test Manager & Is responsible for testing including unit tests, integration tests and usability tests. & Oystein \\ 
  \hline
  Report Manager & Is responsible for delegating and overseeing work on the project report. & Martin \\ 
  \hline
  Customer Representative & Participates in regular meetings to discuss the progress, project status and future tasks. Represents the customer. & Peder Kongelf \\ 
  \hline
  Customer Technical Advisor & May be consulted about technical aspects of the project. & Stig Lau \\ 
  \hline
  Advisor & Serves as a one-man steering committee for the project. & Meng Zhu \\ 
  \hline
  Meeting Secretary & Is responsible for making sure notes get written and sent after each meeting with the advisor and customer. & Oddvar \\ 
  \hline
  Quality Assurance Manager &  & Oystein \\ 
  \hline
  Weekly Report Writer & Is responsible for finalizing the weekly report(s) for the advisor and customer, and getting these delivered for approval. Also responsible for meeting agendas and their delivery. & Oystein \\ 
  \hline
  Time Keeper & Responsible for making sure that everybody is logging their work, and logging team activities. & Oddvar \\ 
  \hline
\end{tabularx}

\section{Communication}
\subsection{Communication rules}
To prevent misunderstanding in communication and

\begin{tabularx}{\textwidth}{ | l | X | }
  \hline
  meeting & scheduled at least 48 hours before, confirmation within 24 hours before meeting required \\ \hline
  documents for the meeting & 24 hours before \\ \hline
  email communication & contact person directly, google groups is just internal \\ \hline
  response from the team & within 8 hours \\ \hline
  response from customer & within 24 hours \\ \hline
\end{tabularx}
\clearpage

\section{Risks}
\begin{tabularx}{\textwidth}{ | l | l | l | l | }
  \hline
  \textbf{#} & \textbf{Risk} & \textbf{Probability} & \textbf{Impact} \\ \hline
  1 & Not getting a fifth party member & M & Significant \\ \hline
  2 & Obtrusive health/family/personal issues for team members & L & Significant \\ \hline
  3 & Low morale in team & M & Significant \\ \hline
  4 & Interfering workload from other activities & H & Minor \\ \hline
  5 & Miscommunication with customer & M & Critical \\ \hline
  6 & Changes in customer requirements & M & Significant \\ \hline
  7 & Errors in project plan & M & Significant \\ \hline
  8 & Failure of communication in team & M & Critical \\ \hline
  9 & Failure of time management & H & Critical \\ \hline
 10 & Errors in workload estimation and distribution & H	Critical \\ \hline
 11 & Failure of online storage systems and services & L	Significant \\ \hline
 12 & Failure of personal computers & M & Significant \\ \hline
 13 & Infeasibility of project as a whole & L & Critical \\ \hline
 14 & Inability to find potential users and test subjects & M & Significant \\ \hline
\end{tabularx}







\section{Meetings}
\section{Lectures}
\section{Issues}


\section{Project plan}
\subsection{Sponsor/customer}
\subsection{Background}
\subsection{Gantt diagram}
\section{Team structure}
\subsection{Roles}
 
\section{Risks}
\section{Architecture}
\section{Scrum}
\section{Quality Assurance}

\section{Domain choosing}
Domain ideas:
project management tool (ehm. redmine)
warehouse
airport / travel agency
cash registers (not interesting)
bank
school information system (boring)
time management system (aka calendar)
facebook console (unreal)
mail interface (gmail is too good, not useful)
photo gallery (limited)
music library (limited)
physician system (treatments, prescriptions, add person)
tax form (boring)
Building management (boring)
Library

(ehm. redmine) 
warehouse 1
1
bank 3 3
(aka calendar) 2
(treatments, prescriptions, add person) 1
Library 2 2 3

Ivo	Martin	Oddvar	Oystein	Total
project management tool	3		2		5
warehouse			1		1
airport / travel agency		1			1
bank		3		3	6
time management system	2				2
physician system	1			1	2
Library		2	3	2	7




Top3:
library
authors, books(location, state), book management, employees, user management, order new books, 

bank
accounts, transfer money, deposits, loans, customer management, employees

project management
projects, issues, work done on issues, workers, sprints, reports, 

interesting	simple to understand	complex enough	ease workflow	existence of power user	total
library	2	3	1	2	Y	8
bank	2	3	2	2	Y	9
project management	1	2	3	2	Y	8



project management
+ usefulness
+ field of study
- boring

library
+ libraries in campus, employees
- simple

bank
- unknown ground


library	project management	bank
martin	3	2	1
oddvar	3	2	1
ivo	2	3	1
oystein	3	1	2
total	11	8	5



Criteria:
Interesting and simple enough for test subjects to understand. something they meet in everyday life
Complicated enough to demonstrate the problem.
Console has to be useful in the domain, ease the workflow
Object oriented design
Existence of power user, that will use the console

Customer ideas:
car models
finn.no
health sector
human resources (people, how they are related, symptoms, how much money and what they own - advanced domain graph). 
contact lists (peder)


write these things to the report


Future:
batch operations
undo the commands
save command for object attribute editing
what about object operations?
transaction support

