\chapter{Requirements}
\section{User stories}
We compiled list of user stories from a few points of view. Administrator section describes mostly detailed technical requirements. General section contains stories applicable on general problem. Domain section contains domain specific user stories.

\subsection{Administrator point of view (section A)}
\begin{enumerate}
  \item As an administrator, I want to be able to store objects in a persistent database, so that I can migrate data easily.
  \item As an administrator, I want to reflect the changes in persistent storage back to user sessions within one second, so the users always see the latest updated data.
  \item As an administrator, I want to be able to work directly with object attributes rather than any form of raw data.
\end{enumerate}

\subsection{User point of view - General (section G)}
\begin{enumerate}
  \item As a user, I want my saved actions to be replicated on to the server within one second, so that my actions will not be lost and the client and server is consistent
  \item As a user, I want my changes to be propagated to other users of the system real- time
  \item As a user, I want to be able to see the console and graphical interface at the same time, so that I can use them both side by side simultaneously.
  \item As a user, I want the changes in console reflect in graphical user interface and likewise, so that I can have overview of the changes I made and I can understand easily, how the system works. In addition this will ensure consistency between the console and graphical interface.
  \item As a user, I want access to a tutorial, so that I can learn to work with the system easily.
  \item As a user, I want to be able to display the currently available commands in the console, so I can easily see what I can do with the objects at hand.
  \item As a user, I want to be able to easily repeat and edit last command, so that I can use it on another object.
  \item As a user, I want to be able to use batch commands, so that I can work with more than one object at the same time.
\end{enumerate}

\subsection{User point of view - Domain specific (section D)}
\begin{enumerate}
  \item As a user, I want to be able to add a new book to the system using both the console and graphical interface.
  \item As a user, I want to be able to delete a book in the system using both the console and graphical interface.
  \item As a user, I want to be able to edit information on a specific book and save these changes using both the console and graphical interface.
  \item As a user, I want to be able to search for a specific book in the system, so that I can watch the information on it using both the console and graphical interface.
  \item As a user, I want to be able to list all the books currently in the system, so that I easily can get an overview of all the books currently in the library. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to registrate a new customer in the system, so that customers can be saved in the system. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to registrate when a customer borrows a book, so that the information is stored in the system. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to edit the information on a specific borrowing of a book, so that any changes can be recorded. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to list all the books currently borrowed, so that I can get information on each of them. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to reserve a book for a customer, so that customers can request and reserve certain books. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to list all the reservations currently in the system. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to view reservations on specific books, so that I can see if a specific book is available for borrowing at the moment. This should be possible in both the console and the graphical interface.
  \item As a user, I want to be able to order new books for the library using both the console and the graphical interface.
\end{enumerate}





\subsection{Planning}
\section{Sequence Diagrams}
\section{Prioritization}
\section{Functional Requirements}
\section{Nonfunctional Requirements}

