\chapter{Sprint 1}
\section{Planning}
We started the sprint with a sprint planning meeting September 24th. The plan for this sprint is to implement a basic implementation of the system, so that we have something to show the customer at the end of the sprint. We chose user stories from the backlog that would enable us to this, a client and server offering only the most basic operations. 

\subsection{Sprint Goal}
The goal for the first sprint is to get a basic version of the library application working. This includes creating a basic GUI with both the graphical web- application and the console side by side, creating a server capable of storing objects and establish communication between the server and client through a basic REST api. The user should be able to use both the web- application and the console to add a new book to the system and to list the books currently in the system. In addition we decided to implement the real- time messaging from the server to the clients to verify that the solution we chose in the pre- study would be up to the task.

\subsection{User stories}
In this sprint we picked the following user stories from the backlog: A1, A2, A3, G3, U1 and U5. 

\begin{table}
\caption{Sprint 1 User Stories}
\centering
\begin{tabular}{ l p{8cm} l l }
\hline 
			&				&\multicolumn{2}{c}{Hours}			\\
 User Story	& Short Description		&Est.		&Act.	                               \\ 
\hline \\ [-2.0ex]
 \bf{A1}     &\bf{Store objects in database}		&\bf{40}		&                                               \\ 
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\

 \bf{A2}     &\bf{Send real- time messages} 		&\bf{25}		&                  \\ 
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\

 \bf{A3}     &\bf{Access to domain specific object} 		&\bf{35}		&		     \\ 
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\

 \bf{G3}     &\bf{Graphical web- application and console}		&\bf{45}		&		     \\ 
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\

 \bf{U1}	   &\bf{Add a new book}		&\bf{30}		&		     \\
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\

 \bf{U5}	   &\bf{List all the books in the system}		&\bf{25}		&		     \\
		  &Design							&			&		\\
		  &Implementation							&			&		\\
		  &Testing						&			&		\\
		  &Documentation						&			&		\\
\hline 
		  &\bf{Total:}			&\bf{200}		&		\\
\hline
\end{tabular}
\label{table:testcasetid01}
\end{table}





\section{Design}
\section{Duration}
\section{Goals}
\section{Testing}
\section{Customer Feedback}
\section{Evaluation}